
\section{Expectations}
This section covers my general expectations of student researchers and lab users, as well as reasonable lab member expectations of me.
%The following section (\S\ref{s:expectations-of-me}) details some reasonable expectations of me. 
Naturally, we will adopt some more detailed expectations of each other over the course of our meetings and discussions. 
Any \emph{written, mutual} agreements arising from those meetings will supersede anything in this document.


\subsection{Conduct \& behavior}
\subsubsection{Trinity University} 
As a student (researcher) at Trinity University, you are always expected to follow \footlink{https://www.trinity.edu/directory/departments-offices/dean-students/conduct}{Trinity's expectations of student conduct} when on-campus, at University events, or acting as a representative of the University.
To be clear, you are a representative of the University whenever you appear as a ``student'' or ``student researcher'' in a professional, academic, or research (including field!) setting. 

\subsubsection{\grackle}

I expect the following conduct from all \grackle{} members.
\begin{enumerate}\setlength{\itemsep}{0ex}
    \item Prioritize the safety and well-being of yourself and others.
    \item Cultivate and sustain an environment of inclusivity, respect, and acceptance.
    \item Provide frequent and \emph{constructive} feedback to your colleagues.
    \item Communicate needs and requests clearly.
\end{enumerate}
Again, I request that you please explicitly communicate your expectations/requests of lab conduct norms to me.
In other words, please let me know how we can support your feeling recognized, respected, and supported in \grackle. 


\subsection{Financial}
You are \emph{never} expected to personally fund research expenses and should always expect those to be covered in full by University or laboratory funds.
This includes travel, lodging, and meals when we travel for research purposes (field, laboratory, conferences).
If you take part in a summer research experience, you will typically be paid a modest stipend (\$500/week), which is to fund your own living expenses. 
In some cases, I can provide compensation for certain research-related work during the academic year, but this is established on a case-by-case basis.

If you have any questions about financial responsibilities or expectations, please ask me!

\subsection{Commitments of time \& effort}\label{s:time}
Scientific understanding rarely (if ever) advances by innate genius or epiphany.
Rather, research progresses through repeated experiments characterized by careful labor and thoughtful evaluation.
Therefore, our research success stems from focused time and effort.

If you are struggling with any of the following expectations, please reach out to me, so that we can develop solutions together.

\paragraph{Time} 
During summer research, I expect you to commit approximately 40~hours (on average) per week, roughly commensurate to five eight-hour workdays. 
During Fall/Spring semesters, time commitments scale with the number of credit hours. 
Table~\ref{t:hours} summarizes typical weekly time expectations.

\begin{table}[b]\centering
    \caption{Typical weekly time expectations for full-time summer research, directed studies (DS with credit hours in parentheses) and thesis research. Summer hours reduce proportionally for holidays.}\label{t:hours}
    \vskip1ex
    \begin{tabular}{lcccc}\toprule
        \bf Commitment & Summer & Thesis/DS(3) & DS(2) & DS(1) \\
        \bf Mean hours/week & 40 & 12 & 8 & 4\\\bottomrule
    \end{tabular}
\end{table}

\paragraph{Effort}
The effort put into research is just as important as the time over which you integrate that effort. When you put time into your research, I expect you to be working \emph{substantively} toward your research goals. Note the term substantive, by which I mean that you are working efficiently, thinking and reflecting critically on your work, and proactively addressing problems/issues as they arise.

\paragraph{Location}
In some cases (lab/field work), you will be working on-site in a field or laboratory setting.
In other cases (reading, coding, writing), your work location may be flexible, and you are welcome to work in locations that are conducive to advancing your goals.
If flexibility becomes detrimental to your productivity, we may mutually revise these expectations. 

\subsubsection{Reasonable expectations of me}
To promote your growth as a scientist, I strive to ensure that you are making the most of your time and effort.
Additionally, the success of your research efforts directly impact the success of my scholarly research program.
You should expect that I will take your time spent conducting research very seriously. 
I will respond in a timely manner to your questions (see \S\ref{s:comm}) and work diligently with you to help overcome obstacles, clarify confusion, and discuss interpretations. 

During summers, I spend the vast majority of my time on our research, so I am routinely on-campus and/or available to answer questions and help troubleshoot.
During Fall/Spring semesters, I have teaching responsibilities that reduce my bandwidth to support your research activity, but I will make every effort to respond promptly and promote your research success.

\subsection{Non-linearity of scientific inquiry}\label{s:sciphi}
Scientific study is highly non-linear.
That is, the amount of time or work you put into science does not directly determine how well your data answers your question. 
Sometimes, small efforts will generate highly informative data, and other times great efforts will generate minimally informative data.
Nature is dynamic, complicated, and stochastic\footnote{Stochasticity is the property of being well-described by a random probability distribution. Stochastic phenomena are characterized by randomness.}; and we have to grapple with that.
Similarly, science is not a set of fixed experimental methods that provide a predictable outcome
In my experience, it is the persistence and responsiveness of our inquiry that ultimately leads to fruitful scientific knowledge.

I encourage you to be persistent, patient, and thoughtfully critical of our methods.
I expect you to be receptive to my feedback, and you should expect me to be receptive to yours. 

\subsubsection{Mistakes, revisions, \& backtracking}
We will make mistakes and revise, backtrack, or give up on some approaches. 
This can be frustrating, but it is a \emph{necessary} component of authentic science, which operates at the edge of knowledge.
We are not omniscient and we learn by doing, so our scientific and personal growth come from learning what works well and what does not. 
This philosophy, in part, motivates my strict policy on artificial intelligence (\S\ref{s:ai}): we want to struggle (an appropriate amount) because that helps us learn.
Beware the fallacy of sunken costs!\footnote{The fallacy of sunken costs is the mistaken belief that one should continue pursuing something simply because they have already sunk costs into it.}

\subsection{Research}
High-quality research is reproducible, precise and accurate, relevant, and thoughtfully interpreted. 
I expect you to pursue all of these as goals/ideals in your research efforts. 
Your research will involve a combination of each of the components listed in the sections below.

\subsubsection{Safety}
Safety of ourselves and others is the single highest priority in our work.
I will address relevant safety concerns in all trainings for any methodology (field, lab, computational), and I will train you how to appropriately practice appropriate safety precautions.

Effective safety cultures are grounded in transparency and trust.
I will never punish someone for accidents or mistakes. 
I expect you to follow all safety protocols, hold your colleagues accountable, and report any safety concerns to me as soon as possible. 
You should expect that I will earnestly, meaningfully, and respectfully respond to your concerns.

\subsubsection{Literature \& background}
Part of your role as a researcher is \emph{continuously} developing your understanding of the field you are working in.
The best way to accomplish this is through routinely engaging with peer-reviewed primary (e.g.~journal articles) and secondary (e.g.~textbooks) literature from the field. 

I expect you to carefully and thoughtfully read all recommended/assigned literature in time for scheduled meetings/discussions. 
In return, you can expect me to help support your access to the literature, answer your questions, teach effective scientific reading techniques, and provide disciplinary context. 

While not explicitly required, I \emph{strongly} recommend that you proactively seek out literature that excites or intrigues you. 
If you feel motivated to take on this challenge but it feels daunting, I will happily nudge you in productive directions.

\subsubsection{Fieldwork}

Coming soon.

\subsubsection{Laboratory work}

Coming soon.

\subsubsection{Data management \& analysis}

Coming soon.
%Paramount

\subsubsection{Interpretations}
Research is an iterative process, where preliminary interpretations of data inform further data collection and analysis. 
Therefore, interpretations are necessary intermediate and ultimate products of our research efforts.
Throughout our research, we will spend time interpreting data (analyses) in the context of prior research and other datasets. 
I expect you to spend time and effort trying to interpret data, and you may expect me to support that process through discussions and advice.


\subsubsection{Writing}
You will occasionally write summaries of your research.
These may take forms that scale from a brief abstract to a multiple-page report to a lengthy thesis. 

I expect you to dedicate sufficient time to prepare legible, coherent, and factually accurate texts;
I expect you to challenge yourself in your writing to become a stronger writer; 
I expect you to use/develop best practices in terms of draft/version and citation management; and 
I expect you to check with me before formally submitting any \grackle-related writing (e.g. abstracts )

You should expect me to provide reasonable notice of writing deadlines (rare exceptions when I learn about things at the last minute); 
you should expect me to provide supportive advice and mentorship during the writing process; and
you should expect me to provide constructive feedback on any lab-related writing that you request.

\paragraph{Feedback timelines} 
In general, I will provide feedback on written material within one~week for large texts ($\gg10^3$~words), 1--3~days for smaller texts ($\le 10^3$~words), or on timelines agreed upon in advance.
I will typically expect similar feedback turnaround times from you.
 

\subsubsection{Publications}
Peer-reviewed publications in academic journals are \emph{the} professional currency in the natural sciences.  
Generally, the ultimate goal of our research efforts is to incorporate our data and interpretations into an article manuscript that gets published.
While we will routinely generate publishable data and interpretations, it will rarely be independently sufficient for publication.
Therefore, you should not \emph{necessarily} expect authorship, though a supporting authorship role is a possibility with sufficient contribution to the project. 
If you are interested in contributing to a publication sufficiently to obtain authorship, let's discuss your goals, interests, and bandwidth.

\subsection{Policy on generative artificial intelligence}\label{s:ai}
You are not permitted to use generative artificial intelligence\footnote{This includes, but is not limited to, large language models like ChatGPT, Claude, and Gemini.} (GenAI) for any \grackle-related research/writing efforts. 
As the PI, I do not permit the use of intellectual property or data generated in \grackle{} to be fed to GenAI algorithms, without explicit prior permission from myself.

I deliberately avoid GenAI for two reasons: GenAIs have profoundly negative environmental impacts and retain the information you feed them. 
I view scientific inquiry, knowledge, and information as a craft rather than a commodity. 
Research and data contexts are important, and GenAIs are neither trustworthy curators of the craft nor its context.
Different researchers have different opinions on the role of GenAI in scientific research, and of course, you are entitled to your own philosophy independent of mine.


\subsection{Communication}\label{s:comm}
Effective, efficient communication will improve every aspect of our collaborative research efforts. 
I am always happy to communicate with lab users\ldots
\begin{enumerate}\setlength{\parskip}{0pt}\setlength{\itemsep}{0pt}
    \item In-person
    \item Over email
    \item Over Trinity Google Chat (in the \texttt{trinity.edu} Gmail interface)
    \item Over a pre-planned zoom or telephone call.
\end{enumerate}

In general, if I am physically on-campus, you should expect asynchronous responses promptly ($\le1$~hour), though this is never guaranteed.
I also maintain a policy that when my office door is open, I welcome spontaneous (albeit brief) conversations.

\subsubsection{Meetings}
We typically meet weekly\footnote{Semiweekly ($2\times$/week) during summers.} for ``regular'' research meetings to discuss research progress, troubleshoot challenges, and set short-term goals. 
We schedule regular meeting times at the beginning of a semester and plan to stick to that schedule throughout.
At (roughly) monthly intervals, we will have an ``executive'' meeting during the scheduled regular meeting time to reflect on research approaches, research progress, and updates to expectations (including expected grades, if relevant).

During summers, we have an additional ``all hands'' laboratory meeting, where all active \grackle{} members meet to discuss readings, learn an important skill, or discuss broader lab topics. 

\subsection{Grades for directed studies and thesis research}\label{s:course}
If you are enrolled in directed studies or thesis research with me, this is tecnically a course.
Unlike typical courses, you will not have formal evaluations (papers, exams) that provide feedback on your progress. 
However, I am required to provide a grade for these to count toward credit. 
Since scientific research is a non-linear process (\S\ref{s:sciphi}), your grade will not be based off of completion of research products but rather effort and persistence toward achieving those. 
You will earn an A by consistently spending (on average) four hours per week per credit hour \emph{substantively} pursuing research goals (see \S\ref{s:time}, Table~\ref{t:hours}). 


