
\section{Getting involved}
The following sections describe what conducting mentored research in \grackle{} typically looks like. 
Please reach out to me directly if you would like to learn more about anything. 
Please note that in all cases, we will explicitly discuss your scientific and professional interests prior to your beginning research of any form under my mentorship.

\subsection{Trinity University students}
\subsubsection{Coursework}
The best way to get to know me and my research interests is by taking one of my courses! 
I bring at least a little bit of my research interests into all of my courses, where you can glimpse this work while developing foundational geoscience knowledge and skills. 

\subsubsection{Summer research}
Summer research experiences are arranged during the academic year. 
The Department of Earth \& Environmental Geosciences runs a competitive application process for summer research positions with its faculty.
Any Trinity student interested in conducting summer research with me  will need to complete this application to be eligible.

A variety of funding pathways from sources within and beyond Trinity University support summer research in \grackle{}.
Typically, students get housing through Trinity, receive a stipend (see \S\ref{s:$}), and receive one credit hour of course credit.
The summer program culminates in a presentation of research findings at the Trinity Summer Research and Internship Symposium. 

\subsubsection{During the academic year}
Some students conduct research during the academic year, typically for-credit as a Directed Studies (GEOS 3190-5/4190-5) or Thesis Research (GEOS~4395-5). 
While the research topics and goals are the same as in the summer, semester-based research tends to be more superficial than the more intensive, focused summer research.
In rare cases, we may coordinate not-for-credit mentored research experiences. 

\subsection{Non-Trinity students}
Student researchers form outside of Trinity University may become involved in GRACkLe through a variety of avenues, including Keck Geology Consortium projects or through direct communication with me.
However, my capacity to support researchers from beyond Trinity is limited by a variety of constraints and depend on available resources and my own bandwidth. 

If you are interested in learning more about \grackle{} from without Trinity University, I encourage you to reach out to me directly, and we can discuss possible opportunities.


%Guidelines on time commitment, tasks and responsibilities are the same as those outlined in the previous section.